Replication of Gantman et al. 2024

### 2024-05-03 manuscript.qmd
Add study 2 models

behavioral_data <- read_csv('data/phase_2/final/behavioral.csv')
```

@@

eeg_data <- read_csv("data/phase_2/final/eeg.csv", col_types = "cdcllcdc")
```

@@

count_good_trials <- eeg_data %>%
  filter(t==0, electrode=="Cz") %>%
  group_by(subject) %>%
  summarize(n=n()) %>%
  mutate(percent = (n/600)*100)

@@

exclude_for_fashion_twice_subjects <- behavioral_data %>%
  filter(phase == "fashion", task == "response") %>%
  group_by(subject_id) %>%
  count() %>%
  filter(n == 600) %>%
  pull(subject_id)
```

@@

exclude_for_eeg_quality <- count_good_trials %>%
  filter(percent < 75) %>%
  pull(subject)
```

@@

subject_non_response_rate <- behavioral_data %>%
  filter(phase == "moral" | phase == "fashion") %>%
  filter(task == "response") %>%
  group_by(subject_id) %>%
  summarise(non_response_rate = mean(is.na(rt)))

exclude_for_non_response_subjects <- subject_non_response_rate %>%
  filter(non_response_rate > 0.5) %>%
  pull(subject_id)
```

@@

subject_non_word_response_rate <- behavioral_data %>%
  filter(phase == "moral" | phase == "fashion") %>%
  filter(task == "response") %>%
  group_by(subject_id) %>%
  mutate(non_word_response = ifelse(
    (is_word == FALSE & correct == TRUE) |
    (is_word == TRUE & correct == FALSE), 1, 0)) %>%
  summarize(non_word_response_rate = mean(non_word_response))

exclude_for_non_word_response_subjects <- subject_non_word_response_rate %>%
  filter(non_word_response_rate > 0.9) %>%
  pull(subject_id)
```

@@

excluded_subjects <- c(exclude_for_fashion_twice_subjects, exclude_for_non_response_subjects, exclude_for_non_word_response_subjects, exclude_for_eeg_quality)

behavioral_data_filtered <- behavioral_data %>%
  filter(!subject_id %in% excluded_subjects)
```

@@

n_subjects <- behavioral_data %>% pull(subject_id) %>% unique() %>% length()

n_subjects_remaining <- behavioral_data_filtered %>% pull(subject_id) %>% unique() %>% length()
```

`r n_subjects` subjects participated in the study. After applying the exclusion criteria, `r n_subjects_remaining` subjects remain. `r length(exclude_for_fashion_twice_subjects)` subjects were excluded for receiving fashion words twice due to a technical error, `r length(exclude_for_eeg_quality)` subjects were excluded for having poor EEG recordings, `r length(exclude_for_non_response_subjects)` subjects were excluded for having a non-response rate greater than 50%, and `r length(exclude_for_non_word_response_subjects)` subjects were excluded for having a non-word response rate greater than 90%.

@@

behavioral_data_test_set <- behavioral_data_filtered %>%
  filter(phase == "moral" | phase == "fashion") %>%
  filter(task == "response") %>%
  select(subject_id, word_type, is_word, correct, rt) %>%
  mutate(word_category = ifelse(word_type %in% c("fashion", "moral"), "category", "non-category"),
         category = ifelse(word_type %in% c("fashion", "non-fashion"), "fashion", "moral"))
```

@@

subject_level_accuracy <- behavioral_data_test_set %>%
  group_by(subject_id, word_category, category, is_word) %>%
  summarise(accuracy = mean(correct), se=sd(correct)/sqrt(n()))
```

@@

behavioral_pop_out_data <- subject_level_accuracy %>%
  filter(is_word == TRUE) %>%
  pivot_wider(names_from = word_category, values_from = c(accuracy, se))

ggplot(behavioral_pop_out_data, aes(x=`accuracy_non-category`, y=`accuracy_category`))+
  geom_point()+
  geom_linerange(aes(ymin=`accuracy_category`-`se_category`, ymax=`accuracy_category`+`se_category`), linewidth=0.25)+
  geom_linerange(aes(xmin=`accuracy_non-category`-`se_non-category`, xmax=`accuracy_non-category`+`se_non-category`), linewidth=0.25, alpha=0.3)+
  labs(x="Accuracy for non-category words", y="Accuracy for category words")+
  facet_grid(.~category, labeller = as_labeller(c("fashion"="Fashion Words", "moral"="Moral Words")))+ 
  geom_abline(intercept = 0, slope = 1, linetype="dashed")+
  coord_cartesian(xlim=c(0.5,1), ylim=c(0.5,1))+
  theme_bw(base_size=12)+
  theme(aspect.ratio=1, panel.grid=element_blank())
```

@@

behavioral_model_moral_pop_out <- gee(correct ~ word_category,
    id = subject_id,
    subset = is_word == TRUE & category == "moral",
    data = behavioral_data_test_set,
    family = binomial,
    corstr = "exchangeable") %>% summary()

coefficient_moral_pop_out <- behavioral_model_moral_pop_out$coefficients[2, 'Estimate']
coefficient_moral_pop_out_se <- behavioral_model_moral_pop_out$coefficients[2, 'Robust S.E.']
z_moral_pop_out <- behavioral_model_moral_pop_out$coefficients[2, 'Robust z']
p_moral_pop_out <- (1 - pnorm(abs(z_moral_pop_out))) * 2

fashion_model_moral_pop_out <- gee(correct ~ word_category,
    id = subject_id,
    subset = is_word == TRUE & category == "fashion",
    data = behavioral_data_test_set,
    family = binomial,
    corstr = "exchangeable") %>% summary()

coefficient_fashion_pop_out <- fashion_model_moral_pop_out$coefficients[2, 'Estimate']
coefficient_fashion_pop_out_se <- fashion_model_moral_pop_out$coefficients[2, 'Robust S.E.']
z_fashion_pop_out <- fashion_model_moral_pop_out$coefficients[2, 'Robust z']
p_fashion_pop_out <- (1 - pnorm(abs(z_fashion_pop_out))) * 2

mean_moral_in_category <- subject_level_accuracy %>%
  filter(is_word == TRUE & category == "moral" & word_category == "category") %>%
  pull(accuracy) %>%
  mean() %>% 
  round(4)* 100

mean_moral_out_category <- subject_level_accuracy %>%
  filter(is_word == TRUE & category == "moral" & word_category == "non-category") %>%
  pull(accuracy) %>%
  mean() %>% 
  round(4)* 100

mean_fashion_in_category <- subject_level_accuracy %>%
  filter(is_word == TRUE & category == "fashion" & word_category == "category") %>%
  pull(accuracy) %>%
  mean() %>% 
  round(4)* 100

mean_fashion_out_category <- subject_level_accuracy %>%
  filter(is_word == TRUE & category == "fashion" & word_category == "non-category") %>%
  pull(accuracy) %>%
  mean() %>% 
  round(4)* 100
```

@@

subject_eeg <- eeg_data %>%
  filter(!subject %in% excluded_subjects) %>%
  filter(electrode %in% c("Cz", "Pz")) %>%
  filter(correct == TRUE) %>%
  group_by(subject, t, electrode, word_type, is_word) %>%
  summarize(v = mean(v), n=n()) %>%
  mutate(word_category = ifelse(word_type %in% c("fashion", "moral"), "category", "non-category"),
         category = ifelse(word_type %in% c("fashion", "non-fashion"), "fashion", "moral"))
```

@@

grand_average <- subject_eeg %>%
  group_by(t, electrode, word_category, category, is_word) %>%
  summarize(M = mean(v), SE = sd(v)/sqrt(n()))
```

@@

ggplot(grand_average, aes(x=t, y=M, color=is_word, linetype=word_category)) +
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  geom_vline(xintercept = c(200, 250, 350, 600, 800), linetype="dotted", alpha=0.6)+
  geom_ribbon(aes(ymin=M-SE, ymax=M+SE, fill=is_word), alpha=0.2, color=NA)+
  geom_line()+
  scale_x_continuous(breaks=c(0,500, 1000))+
  scale_color_brewer(palette="Set1", name="Is word?", labels=c("Non-word", "Word"))+
  scale_fill_brewer(palette="Set1", name="Is word?", labels=c("Non-word", "Word"))+
  scale_linetype_manual(name="Word Category", labels=c("Moral/Fashion", "Non-Moral/Non-Fashion"), values=c("solid", "dashed"))+
  facet_grid(electrode~category, labeller=as_labeller(c("fashion"="Fashion Words", "moral"="Moral Words", "Cz"="Cz", "Pz"="Pz" )))+
  labs(x="Time since word onset (ms)", y="Voltage (uV)", color="Is word?", fill="Is word?", linetype="Word Category")+
  theme_minimal(base_size=12)+
  theme(panel.grid = element_blank())
```

@@

time_window_data <- eeg_data %>%
  filter(!subject %in% excluded_subjects) %>%
  filter(electrode %in% c("Cz", "Pz")) %>%
  mutate(erp_component = get_time_window(t)) %>%
  filter(erp_component != "other") %>%
  group_by(subject, electrode, word_type, is_word, erp_component) %>%
  summarize(v = mean(v)) %>%
  mutate(word_category = ifelse(word_type %in% c("fashion", "moral"), "category", "non-category"),
         category = ifelse(word_type %in% c("fashion", "non-fashion"), "fashion", "moral"))
```

>>>>

behavioral_data_study_2 <- read_csv('data/phase_2/final/behavioral.csv')
```

@@

eeg_data_study_2 <- read_csv("data/phase_2/final/eeg.csv", col_types = "cdcllcdc")
```

@@

count_good_trials_study_2 <- eeg_data_study_2 %>%
  filter(t==0, electrode=="Cz") %>%
  group_by(subject) %>%
  summarize(n=n()) %>%
  mutate(percent = (n/600)*100)

@@

exclude_for_fashion_twice_subjects_study_2 <- behavioral_data_study_2 %>%
  filter(phase == "fashion", task == "response") %>%
  group_by(subject_id) %>%
  count() %>%
  filter(n == 600) %>%
  pull(subject_id)
```

```{r} 
#| label: Filter out a subject who saw the first 100 trials twice because of EEG recording error
#| include: false

exclude_for_repeated_viewing_study_2 <- c("14")
```

@@

exclude_for_eeg_quality_study_2 <- count_good_trials_study_2 %>%
  filter(percent < 75) %>%
  pull(subject)
```

@@

subject_non_response_rate_study_2 <- behavioral_data_study_2 %>%
  filter(phase == "moral" | phase == "fashion") %>%
  filter(task == "response") %>%
  group_by(subject_id) %>%
  summarise(non_response_rate = mean(is.na(rt)))

exclude_for_non_response_subjects_study_2 <- subject_non_response_rate_study_2 %>%
  filter(non_response_rate > 0.5) %>%
  pull(subject_id)
```

@@

subject_non_word_response_rate_study_2 <- behavioral_data_study_2 %>%
  filter(phase == "moral" | phase == "fashion") %>%
  filter(task == "response") %>%
  group_by(subject_id) %>%
  mutate(non_word_response = ifelse(
    (is_word == FALSE & correct == TRUE) |
    (is_word == TRUE & correct == FALSE), 1, 0)) %>%
  summarize(non_word_response_rate = mean(non_word_response))

exclude_for_non_word_response_subjects_study_2 <- subject_non_word_response_rate_study_2 %>%
  filter(non_word_response_rate > 0.9) %>%
  pull(subject_id)
```

@@

excluded_subjects_study_2 <- c(
  exclude_for_fashion_twice_subjects_study_2, 
  exclude_for_non_response_subjects_study_2, 
  exclude_for_non_word_response_subjects_study_2, 
  exclude_for_eeg_quality_study_2,
  exclude_for_repeated_viewing_study_2
)

behavioral_data_filtered_study_2 <- behavioral_data_study_2 %>%
  filter(!subject_id %in% excluded_subjects_study_2)
```

@@

n_subjects_study_2 <- behavioral_data_study_2 %>% pull(subject_id) %>% unique() %>% length()

n_subjects_remaining_study_2 <- behavioral_data_filtered_study_2 %>% pull(subject_id) %>% unique() %>% length()
```

`r n_subjects_study_2` subjects participated in the study. After applying the exclusion criteria, `r n_subjects_remaining_study_2` subjects remain. `r length(exclude_for_fashion_twice_subjects_study_2)` subject was excluded for receiving fashion words twice due to a technical error, `r length(exclude_for_repeated_viewing_study_2)` subject was excluded because they saw the first 100 trials twice due to an EEG data recording error, `r length(exclude_for_eeg_quality_study_2)` subjects were excluded for having poor EEG recordings, `r length(exclude_for_non_response_subjects_study_2)` subjects were excluded for having a non-response rate greater than 50%, and `r length(exclude_for_non_word_response_subjects_study_2)` subjects were excluded for having a non-word response rate greater than 90%.

@@

behavioral_data_test_set_study_2 <- behavioral_data_filtered_study_2 %>%
  filter(phase == "moral" | phase == "fashion") %>%
  filter(task == "response") %>%
  select(subject_id, word_type, is_word, correct, rt) %>%
  mutate(word_category = ifelse(word_type %in% c("fashion", "moral"), "category", "non-category"),
         category = ifelse(word_type %in% c("fashion", "non-fashion"), "fashion", "moral"))
```

@@

subject_level_accuracy_study_2 <- behavioral_data_test_set_study_2 %>%
  group_by(subject_id, word_category, category, is_word) %>%
  summarise(accuracy = mean(correct), se=sd(correct)/sqrt(n()))
```

@@

behavioral_pop_out_data_study_2 <- subject_level_accuracy_study_2 %>%
  filter(is_word == TRUE) %>%
  pivot_wider(names_from = word_category, values_from = c(accuracy, se))

ggplot(behavioral_pop_out_data_study_2, aes(x=`accuracy_non-category`, y=`accuracy_category`))+
  geom_point()+
  geom_linerange(aes(ymin=`accuracy_category`-`se_category`, ymax=`accuracy_category`+`se_category`), linewidth=0.25)+
  geom_linerange(aes(xmin=`accuracy_non-category`-`se_non-category`, xmax=`accuracy_non-category`+`se_non-category`), linewidth=0.25, alpha=0.3)+
  labs(x="Accuracy for non-category words", y="Accuracy for category words")+
  facet_grid(.~category, labeller = as_labeller(c("fashion"="Fashion Words", "moral"="Moral Words")))+ 
  geom_abline(intercept = 0, slope = 1, linetype="dashed")+
  coord_cartesian(xlim=c(0.5,1), ylim=c(0.5,1))+
  theme_bw(base_size=12)+
  theme(aspect.ratio=1, panel.grid=element_blank())
```

@@

behavioral_model_moral_pop_out_study_2 <- gee(correct ~ word_category,
    id = subject_id,
    subset = is_word == TRUE & category == "moral",
    data = behavioral_data_test_set_study_2,
    family = binomial,
    corstr = "exchangeable") %>% summary()

coefficient_moral_pop_out_study_2 <- behavioral_model_moral_pop_out_study_2$coefficients[2, 'Estimate']
coefficient_moral_pop_out_se_study_2 <- behavioral_model_moral_pop_out_study_2$coefficients[2, 'Robust S.E.']
z_moral_pop_out_study_2 <- behavioral_model_moral_pop_out_study_2$coefficients[2, 'Robust z']
p_moral_pop_out_study_2 <- (1 - pnorm(abs(z_moral_pop_out_study_2))) * 2

fashion_model_moral_pop_out_study_2 <- gee(correct ~ word_category,
    id = subject_id,
    subset = is_word == TRUE & category == "fashion",
    data = behavioral_data_test_set_study_2,
    family = binomial,
    corstr = "exchangeable") %>% summary()

coefficient_fashion_pop_out_study_2 <- fashion_model_moral_pop_out_study_2$coefficients[2, 'Estimate']
coefficient_fashion_pop_out_se_study_2 <- fashion_model_moral_pop_out_study_2$coefficients[2, 'Robust S.E.']
z_fashion_pop_out_study_2 <- fashion_model_moral_pop_out_study_2$coefficients[2, 'Robust z']
p_fashion_pop_out_study_2 <- (1 - pnorm(abs(z_fashion_pop_out_study_2))) * 2

mean_moral_in_category_study_2 <- subject_level_accuracy_study_2 %>%
  filter(is_word == TRUE & category == "moral" & word_category == "category") %>%
  pull(accuracy) %>%
  mean() %>% 
  round(4)* 100

mean_moral_out_category_study_2 <- subject_level_accuracy_study_2 %>%
  filter(is_word == TRUE & category == "moral" & word_category == "non-category") %>%
  pull(accuracy) %>%
  mean() %>% 
  round(4)* 100

mean_fashion_in_category_study_2 <- subject_level_accuracy_study_2 %>%
  filter(is_word == TRUE & category == "fashion" & word_category == "category") %>%
  pull(accuracy) %>%
  mean() %>% 
  round(4)* 100

mean_fashion_out_category_study_2 <- subject_level_accuracy_study_2 %>%
  filter(is_word == TRUE & category == "fashion" & word_category == "non-category") %>%
  pull(accuracy) %>%
  mean() %>% 
  round(4)* 100
```

In the moral condition, participants were `r mean_moral_in_category_study_2`% accurate for moral words and `r mean_moral_out_category_study_2`% accurate for non-moral words. This difference was not statistically significant in the GEE model, $\beta$ = `r coefficient_moral_pop_out_study_2 %>% round(3)`, *SE* = `r coefficient_moral_pop_out_se_study_2 %>% round(3)`, *z* = `r z_moral_pop_out_study_2 %>% round(3)`, *p* = `r p_moral_pop_out_study_2 %>% format(scientific=FALSE)`.

In the fashion condition, participants were `r mean_fashion_in_category_study_2`% accurate for fashion words and `r mean_fashion_out_category_study_2`% accurate for non-fashion words.  This difference was statistically significant in the GEE model, $\beta$ = `r coefficient_fashion_pop_out_study_2`, *SE* = `r coefficient_fashion_pop_out_se_study_2 %>% round(3)`, *z* = `r z_fashion_pop_out_study_2 %>% round(3)`, *p* = `r p_fashion_pop_out_study_2 %>% format(scientific=FALSE)`.

@@

subject_eeg_study_2 <- eeg_data_study_2 %>%
  filter(!subject %in% excluded_subjects_study_2) %>%
  filter(electrode %in% c("Cz", "Pz")) %>%
  filter(correct == TRUE) %>%
  group_by(subject, t, electrode, word_type, is_word) %>%
  summarize(v = mean(v), n=n()) %>%
  mutate(word_category = ifelse(word_type %in% c("fashion", "moral"), "category", "non-category"),
         category = ifelse(word_type %in% c("fashion", "non-fashion"), "fashion", "moral"))
```

@@

grand_average_study_2 <- subject_eeg_study_2 %>%
  group_by(t, electrode, word_category, category, is_word) %>%
  summarize(M = mean(v), SE = sd(v)/sqrt(n()))
```

@@

ggplot(grand_average_study_2, aes(x=t, y=M, color=is_word, linetype=word_category)) +
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  geom_vline(xintercept = c(200, 250, 350, 600, 800), linetype="dotted", alpha=0.6)+
  geom_ribbon(aes(ymin=M-SE, ymax=M+SE, fill=is_word), alpha=0.2, color=NA)+
  geom_line()+
  scale_x_continuous(breaks=c(0,500, 1000))+
  scale_color_brewer(palette="Set1", name="Is word?", labels=c("Non-word", "Word"))+
  scale_fill_brewer(palette="Set1", name="Is word?", labels=c("Non-word", "Word"))+
  scale_linetype_manual(name="Word Category", labels=c("Moral/Fashion", "Non-Moral/Non-Fashion"), values=c("solid", "dashed"))+
  facet_grid(electrode~category, labeller=as_labeller(c("fashion"="Fashion Words", "moral"="Moral Words", "Cz"="Cz", "Pz"="Pz" )))+
  labs(x="Time since word onset (ms)", y="Voltage (uV)", color="Is word?", fill="Is word?", linetype="Word Category")+
  theme_minimal(base_size=12)+
  theme(panel.grid = element_blank())
```

@@

time_window_data_study_2 <- eeg_data_study_2 %>%
  filter(!subject %in% excluded_subjects_study_2) %>%
  filter(electrode %in% c("Cz", "Pz")) %>%
  mutate(erp_component = get_time_window(t)) %>%
  filter(erp_component != "other") %>%
  group_by(subject, electrode, word_type, is_word, erp_component) %>%
  summarize(v = mean(v)) %>%
  mutate(word_category = ifelse(word_type %in% c("fashion", "moral"), "category", "non-category"),
         category = ifelse(word_type %in% c("fashion", "non-fashion"), "fashion", "moral"))
```

```{r}
#| label: Run GEE models for all time windows, moral data word non-word, study 2
#| include: false

p2_model_moral_word_nonword_study_2 <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "p2" & category == "moral" & electrode == "Pz",
    data = time_window_data_study_2,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p2_model_moral_word_nonword_beta_study_2 <- p2_model_moral_word_nonword_study_2$coefficients[2, 'Estimate']
p2_model_moral_word_nonword_se_study_2 <- p2_model_moral_word_nonword_study_2$coefficients[2, 'Robust S.E.']
p2_model_moral_word_nonword_z_study_2 <- p2_model_moral_word_nonword_study_2$coefficients[2, 'Robust z']
p2_model_moral_word_nonword_p_study_2 <- (1 - pnorm(abs(p2_model_moral_word_nonword_z_study_2))) * 2

n2_model_moral_word_nonword_study_2 <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "n2" & category == "moral" & electrode == "Pz",
    data = time_window_data_study_2,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

n2_model_moral_word_nonword_beta_study_2 <- n2_model_moral_word_nonword_study_2$coefficients[2, 'Estimate']
n2_model_moral_word_nonword_se_study_2 <- n2_model_moral_word_nonword_study_2$coefficients[2, 'Robust S.E.']
n2_model_moral_word_nonword_z_study_2 <- n2_model_moral_word_nonword_study_2$coefficients[2, 'Robust z']
n2_model_moral_word_nonword_p_study_2 <- (1 - pnorm(abs(n2_model_moral_word_nonword_z_study_2))) * 2

p3_model_moral_word_nonword_study_2 <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "p3" & category == "moral" & electrode == "Pz",
    data = time_window_data_study_2,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p3_model_moral_word_nonword_beta_study_2 <- p3_model_moral_word_nonword_study_2$coefficients[2, 'Estimate']
p3_model_moral_word_nonword_se_study_2 <- p3_model_moral_word_nonword_study_2$coefficients[2, 'Robust S.E.']
p3_model_moral_word_nonword_z_study_2 <- p3_model_moral_word_nonword_study_2$coefficients[2, 'Robust z']
p3_model_moral_word_nonword_p_study_2 <- (1 - pnorm(abs(p3_model_moral_word_nonword_z_study_2))) * 2

lpp_model_moral_word_nonword_study_2 <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "lpp" & category == "moral" & electrode == "Pz",
    data = time_window_data_study_2,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

lpp_model_moral_word_nonword_beta_study_2 <- lpp_model_moral_word_nonword_study_2$coefficients[2, 'Estimate']
lpp_model_moral_word_nonword_se_study_2 <- lpp_model_moral_word_nonword_study_2$coefficients[2, 'Robust S.E.']
lpp_model_moral_word_nonword_z_study_2 <- lpp_model_moral_word_nonword_study_2$coefficients[2, 'Robust z']
lpp_model_moral_word_nonword_p_study_2 <- (1 - pnorm(abs(lpp_model_moral_word_nonword_z_study_2))) * 2
```

In the moral condition, words elicited a more positive ERP in the P2 window ($\beta$ = `r p2_model_moral_word_nonword_beta_study_2 %>% round(3)`, *SE* = `r p2_model_moral_word_nonword_se_study_2 %>% round(3)`, *z* = `r p2_model_moral_word_nonword_z_study_2 %>% round(3)`, *p* = `r p2_model_moral_word_nonword_p_study_2 %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_moral_word_nonword_beta_study_2 %>% round(3)`, *SE* = `r n2_model_moral_word_nonword_se_study_2 %>% round(3)`, *z* = `r n2_model_moral_word_nonword_z_study_2 %>% round(3)`, *p* = `r n2_model_moral_word_nonword_p_study_2 %>% format(scientific=FALSE)`), and P3 window ($\beta$ = `r p3_model_moral_word_nonword_beta_study_2 %>% round(3)`, *SE* = `r p3_model_moral_word_nonword_se_study_2 %>% round(3)`, *z* = `r p3_model_moral_word_nonword_z_study_2 %>% round(3)`, *p* = `r p3_model_moral_word_nonword_p_study_2 %>% format(scientific=FALSE)`). There was no significant effect in the LPP window ($\beta$ = `r lpp_model_moral_word_nonword_beta_study_2 %>% round(3)`, *SE* = `r lpp_model_moral_word_nonword_se_study_2 %>% round(3)`, *z* = `r lpp_model_moral_word_nonword_z_study_2 %>% round(3)`, *p* = `r lpp_model_moral_word_nonword_p_study_2 %>% format(scientific=FALSE)`).

```{r}
#| label: Run GEE models for all time windows, fashion data word non-word, study 2
#| include: false

p2_model_fashion_word_nonword_study_2 <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "p2" & category == "fashion" & electrode == "Pz",
    data = time_window_data_study_2,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p2_model_fashion_word_nonword_beta_study_2 <- p2_model_fashion_word_nonword_study_2$coefficients[2, 'Estimate']
p2_model_fashion_word_nonword_se_study_2 <- p2_model_fashion_word_nonword_study_2$coefficients[2, 'Robust S.E.']
p2_model_fashion_word_nonword_z_study_2 <- p2_model_fashion_word_nonword_study_2$coefficients[2, 'Robust z']
p2_model_fashion_word_nonword_p_study_2 <- (1 - pnorm(abs(p2_model_fashion_word_nonword_z_study_2))) * 2

n2_model_fashion_word_nonword_study_2 <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "n2" & category == "fashion" & electrode == "Pz",
    data = time_window_data_study_2,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

n2_model_fashion_word_nonword_beta_study_2 <- n2_model_fashion_word_nonword_study_2$coefficients[2, 'Estimate']
n2_model_fashion_word_nonword_se_study_2 <- n2_model_fashion_word_nonword_study_2$coefficients[2, 'Robust S.E.']
n2_model_fashion_word_nonword_z_study_2 <- n2_model_fashion_word_nonword_study_2$coefficients[2, 'Robust z']
n2_model_fashion_word_nonword_p_study_2 <- (1 - pnorm(abs(n2_model_fashion_word_nonword_z_study_2))) * 2

p3_model_fashion_word_nonword_study_2 <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "p3" & category == "fashion" & electrode == "Pz",
    data = time_window_data_study_2,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p3_model_fashion_word_nonword_beta_study_2 <- p3_model_fashion_word_nonword_study_2$coefficients[2, 'Estimate']
p3_model_fashion_word_nonword_se_study_2 <- p3_model_fashion_word_nonword_study_2$coefficients[2, 'Robust S.E.']
p3_model_fashion_word_nonword_z_study_2 <- p3_model_fashion_word_nonword_study_2$coefficients[2, 'Robust z']
p3_model_fashion_word_nonword_p_study_2 <- (1 - pnorm(abs(p3_model_fashion_word_nonword_z_study_2))) * 2

lpp_model_fashion_word_nonword_study_2 <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "lpp" & category == "fashion" & electrode == "Pz",
    data = time_window_data_study_2,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

lpp_model_fashion_word_nonword_beta_study_2 <- lpp_model_fashion_word_nonword_study_2$coefficients[2, 'Estimate']
lpp_model_fashion_word_nonword_se_study_2 <- lpp_model_fashion_word_nonword_study_2$coefficients[2, 'Robust S.E.']
lpp_model_fashion_word_nonword_z_study_2 <- lpp_model_fashion_word_nonword_study_2$coefficients[2, 'Robust z']
lpp_model_fashion_word_nonword_p_study_2 <- (1 - pnorm(abs(lpp_model_fashion_word_nonword_z_study_2))) * 2

In the fashion condition, there was no significant difference in any of the time windows; P2 window ($\beta$ = `r p2_model_fashion_word_nonword_beta_study_2 %>% round(3)`, *SE* = `r p2_model_fashion_word_nonword_se_study_2 %>% round(3)`, *z* = `r p2_model_fashion_word_nonword_z_study_2 %>% round(3)`, *p* = `r p2_model_fashion_word_nonword_p_study_2 %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_fashion_word_nonword_beta_study_2 %>% round(3)`, *SE* = `r n2_model_fashion_word_nonword_se_study_2 %>% round(3)`, *z* = `r n2_model_fashion_word_nonword_z_study_2 %>% round(3)`, *p* = `r n2_model_fashion_word_nonword_p_study_2 %>% format(scientific=FALSE)`), P3 window ($\beta$ = `r p3_model_fashion_word_nonword_beta_study_2 %>% round(3)`, *SE* = `r p3_model_fashion_word_nonword_se_study_2 %>% round(3)`, *z* = `r p3_model_fashion_word_nonword_z_study_2 %>% round(3)`, *p* = `r p3_model_fashion_word_nonword_p_study_2 %>% format(scientific=FALSE)`), and LPP window ($\beta$ = `r lpp_model_fashion_word_nonword_beta_study_2 %>% round(3)`, *SE* = `r lpp_model_fashion_word_nonword_se_study_2 %>% round(3)`, *z* = `r lpp_model_fashion_word_nonword_z_study_2 %>% round(3)`, *p* = `r lpp_model_fashion_word_nonword_p_study_2 %>% format(scientific=FALSE)`).

```{r}
#| label: Run GEE models for all time windows, moral data pop-out, study 2
#| include: false

p2_model_moral_popout_study_2 <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "p2" & category == "moral" & is_word == TRUE & electrode == "Cz",
    data = time_window_data_study_2,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p2_model_moral_popout_beta_study_2 <- p2_model_moral_popout_study_2$coefficients[2, 'Estimate']
p2_model_moral_popout_se_study_2 <- p2_model_moral_popout_study_2$coefficients[2, 'Robust S.E.']
p2_model_moral_popout_z_study_2 <- p2_model_moral_popout_study_2$coefficients[2, 'Robust z']
p2_model_moral_popout_p_study_2 <- (1 - pnorm(abs(p2_model_moral_popout_z_study_2))) * 2

n2_model_moral_popout_study_2 <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "n2" & category == "moral" & is_word == TRUE & electrode == "Cz",
    data = time_window_data_study_2,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

n2_model_moral_popout_beta_study_2 <- n2_model_moral_popout_study_2$coefficients[2, 'Estimate']
n2_model_moral_popout_se_study_2 <- n2_model_moral_popout_study_2$coefficients[2, 'Robust S.E.']
n2_model_moral_popout_z_study_2 <- n2_model_moral_popout_study_2$coefficients[2, 'Robust z']
n2_model_moral_popout_p_study_2 <- (1 - pnorm(abs(n2_model_moral_popout_z_study_2))) * 2

p3_model_moral_popout_study_2 <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "p3" & category == "moral"& is_word == TRUE & electrode == "Cz",
    data = time_window_data_study_2,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p3_model_moral_popout_beta_study_2 <- p3_model_moral_popout_study_2$coefficients[2, 'Estimate']
p3_model_moral_popout_se_study_2 <- p3_model_moral_popout_study_2$coefficients[2, 'Robust S.E.']
p3_model_moral_popout_z_study_2 <- p3_model_moral_popout_study_2$coefficients[2, 'Robust z']
p3_model_moral_popout_p_study_2 <- (1 - pnorm(abs(p3_model_moral_popout_z_study_2))) * 2

lpp_model_moral_popout_study_2 <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "lpp" & category == "moral"& is_word == TRUE & electrode == "Cz",
    data = time_window_data_study_2,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

lpp_model_moral_popout_beta_study_2 <- lpp_model_moral_popout_study_2$coefficients[2, 'Estimate']
lpp_model_moral_popout_se_study_2 <- lpp_model_moral_popout_study_2$coefficients[2, 'Robust S.E.']
lpp_model_moral_popout_z_study_2 <- lpp_model_moral_popout_study_2$coefficients[2, 'Robust z']
lpp_model_moral_popout_p_study_2 <- (1 - pnorm(abs(lpp_model_moral_popout_z_study_2))) * 2

In the moral condition, there was a significant difference between moral and non-moral words in the P2 window ($\beta$ = `r p2_model_moral_popout_beta_study_2 %>% round(3)`, *SE* = `r p2_model_moral_popout_se_study_2 %>% round(3)`, *z* = `r p2_model_moral_popout_z_study_2 %>% round(3)`, *p* = `r p2_model_moral_popout_p_study_2 %>% format(scientific=FALSE)`), but this difference was in the opposite direction predicted by Gantman et al. (2020). There were no significant differences between moral and non-moral words in the N2 window ($\beta$ = `r n2_model_moral_popout_beta_study_2 %>% round(3)`, *SE* = `r n2_model_moral_popout_se_study_2 %>% round(3)`, *z* = `r n2_model_moral_popout_z_study_2 %>% round(3)`, *p* = `r n2_model_moral_popout_p_study_2 %>% format(scientific=FALSE)`), P3 window ($\beta$ = `r p3_model_moral_popout_beta_study_2 %>% round(3)`, *SE* = `r p3_model_moral_popout_se_study_2 %>% round(3)`, *z* = `r p3_model_moral_popout_z_study_2 %>% round(3)`, *p* = `r p3_model_moral_popout_p_study_2 %>% format(scientific=FALSE)`), and the LPP window ($\beta$ = `r lpp_model_moral_popout_beta_study_2 %>% round(3)`, *SE* = `r lpp_model_moral_popout_se_study_2 %>% round(3)`, *z* = `r lpp_model_moral_popout_z_study_2 %>% round(3)`, *p* = `r lpp_model_moral_popout_p_study_2 %>% format(scientific=FALSE)`).

```{r}
#| label: Run GEE models for all time windows, fashion data pop-out, study 2
#| include: false

p2_model_fashion_popout_study_2 <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "p2" & category == "fashion" & is_word == TRUE & electrode == "Cz",
    data = time_window_data_study_2,
    family = gaussian,
    corstr = "exchangeable") %>% summary()
